Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2017-08-18 stp/paper_aaai/main.tex
Writing bits

% natalia
\usepackage{multirow}

@@

An ontology $\mathcal{O}$ is a specification of classes of objects, their 
data properties and relationships between them.
An example of an ontology is given in Fig. \ref{FIG:onto}. 
A Class in an ontology can have \emph{data properties} or \emph{object properties}. 
For example an ``Organisation'' has a ``Person'' 
(which is a class with its own properties), and it has a ``name'' (which 
is a data property). 
Also, a Class can be a subclass of another Class. 
For 
example ``Cities'' and ``States'' are both ``Places''. 
A subclass inherits all the properties of the parent class.

A \emph{semantic model} $m$ is a directed graph with two types of nodes: 
\emph{class nodes} and \emph{data nodes}. 
We denote them as $\mathcal{C}_m$ and $\mathcal{D}_m$ respectively.
 We define $\mathcal{N}_m = \mathcal{C}_m \cup 
\mathcal{D}_m$. $ \mathcal{C}_m$ corresponds to classes in the ontology 
$\mathcal{O}$. $\mathcal{D}_m$ corresponds to data 
properties in the ontology. 
The edges in the semantic model correspond to relationships in the ontology, as shown if Figures \ref{FIG:onto} and \ref{FIG:sem}.

@@

In our context, we define a \emph{pattern} is a graph $P$ that is undirected 
and simple (no multiple edges between two nodes, nor self-loops).

@@

@@

\subsection{Modeling \relonto{} in CP}
In order to model this problem we used the \minizinc{} language 
\cite{minizinc}, and the 
\chuffed{} solver \cite{chu2011improving} because it has a global constraint 
implemented for Steiner 
Tree Problems \cite{deuna2016steiner}.

@@

@@

@@

\section{Related Work \label{SEC:pw}}
\ddg{rewrite, add more}

@@

@@

\bibliographystyle{aaai}
\npr{shorten citations}
\bibliography{main}
\end{document}

>>>>

% natalia
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{multirow}
\usepackage{pgfplots}
\pgfplotsset{width=10cm,compat=1.9}
\usepgfplotslibrary{colorbrewer}

@@

An ontology $\mathcal{O}$ is a specification of classes of objects, their 
data properties and relationships between them.
An example of an ontology is given in Fig.~\ref{FIG:onto}. 
A Class in an ontology can have \emph{data properties} or \emph{object properties}. 
For example, an ``Organisation'' has a ``Person'' 
(which is a class with its own properties), and it has a ``name'' (which 
is a data property). 
Also, a Class can be a subclass of another Class. 
For 
example ``Cities'' and ``States'' are both ``Places''. 
A subclass inherits all the properties of the parent class.
\npr{rephrase, I think terminology is off}

A \emph{semantic model} $m$ is a directed graph with two types of nodes: 
\emph{class nodes} and \emph{data nodes}. 
We denote them as $\mathcal{C}_m$ and $\mathcal{D}_m$ respectively.
 We define $\mathcal{N}_m = \mathcal{C}_m \cup 
\mathcal{D}_m$. $ \mathcal{C}_m$ corresponds to classes in the ontology 
$\mathcal{O}$. $\mathcal{D}_m$ corresponds to data 
properties in the ontology. 
The edges in the semantic model correspond to relationships in the ontology, as shown if Fig.~\ref{FIG:onto} and \ref{FIG:sem}.

@@

\npr{reformulate for typed directed multigraphs and example based on Fig3}
In our context, we define a \emph{pattern} is a graph $P$ that is undirected 
and simple (no multiple edges between two nodes, nor self-loops).

@@

We obtain patterns of size upto 6 in under 4 minutes for the biggest instances in our evaluation framework. \npr{Elaborate more, karma's approach for pattern mining took 1 hour, maybe cite my work on how databases perform for graph pattern matching}

@@

\subsection{\relonto{} in Constraint Programming}
In order to model this problem we used the \minizinc{} language 
\cite{minizinc}, and the 
\chuffed{} solver \cite{chu2011improving} because it has a global constraint 
implemented for Steiner 
Tree Problems \cite{deuna2016steiner}.

@@

We have run all our experiments on a Dell server with 252 GiB of memory, 2 CPUs with 4 cores each, 1 Titan GPU and 1 GeForce 1080 Ti GPU.
\npr{check characteristics}

@@

We have developed a new approach for semantic labeling which can efficiently handle the \emph{unknown} class.
We demonstrate its efficiency by comparing against the state-of-the-art approach DSL~\cite{Pham:semantic}.
\npr{Explain}

@@

\begin{figure*}[ht]\small
\pgfplotsset{
    small,
    %legend style={legend pos=north east}
    legend style={
        at={(0.01,0.01)},
        anchor=south west,
    },
   }%
\begin{minipage}[b]{.5\linewidth}
\centering
\begin{tikzpicture}[baseline]
\begin{axis}[
		    xlabel={\emph{numBags}},
		    ylabel={Performance (MRR)},
		    xmin=0, xmax=150,
		    ymin=0.5, ymax=1,
		    xtick={0,10,50,100,150},
		    ytick={0.5,0.6,0.7,0.8,0.9,1},
		    legend pos=south east,
		    ymajorgrids=true,
		    grid style=dashed
		]

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (10, 0.85154623154623166)(50, 0.85902097902097896)(100,0.87487956487956486)(150,0.8802331002331002)
		    };
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (10,  0.73272601851632158)(50, 0.73596072887032105)(100,0.73736629035127532)(150,0.73512315058140676)
		    };
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (10,  0.53396973928187841)(50, 0.56218126081141884)(100,0.55857468339226135)(150,0.55938671902457904)
		    };
		 \addplot[
		    color=brown,
		    mark=+,
		    ]
		    coordinates {
		    (10,  0.81292733659634253)(50, 0.81182668838989458)(100, 0.80705336361770219)(150,0.80801980454223066)
		    };
		 \addplot[
		    color=violet,
		    mark=star,
		    ]
		    coordinates {
		    (10,   0.87823326846764416)(50, 0.89727564102564272)(100,0.9136698717948738)(150,0.91708333333333425)
		    };
		%\legend{weather,weapons,soccer,museum,city}

		\end{axis}
\end{tikzpicture}
\subcaption{fixing \emph{bagSize}=100}\label{fig:numbags}
\end{minipage}%
%
\begin{minipage}[b]{.5\linewidth}
\centering
\begin{tikzpicture}[baseline]
		\begin{axis}[
		    xlabel={\emph{bagSize}},
		    %ylabel={Performance (MRR)},
		    xmin=0, xmax=100,
		    ymin=0.5, ymax=1,
		    xtick={0,10,30,50,100},
		    ytick={0.5,0.6,0.7,0.8,0.9,1},
		    legend pos=outer north east,
		    ymajorgrids=true,
		    grid style=dashed
		]

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (10, 0.88427350427350415)(30,  0.9027583527583527)(50,0.91336441336441332)(100,0.87871794871794873)
		    };
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (10,  0.75910921069769555)(30, 0.76156533626682754)(50,0.75502218858295522)(100,0.75538165183154382)
		    };
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (10,  0.56646107828012637)(30, 0.5693901714881866)(50,0.58629781920572777)(100,0.58408351395802571)
		    };
		 \addplot[
		    color=brown,
		    mark=+,
		    ]
		    coordinates {
		    (10,  0.78552344907839267)(30, 0.78870711278952932)(50,0.78519302797324753)(100,0.77792094596490047)
		    };
		 \addplot[
		    color=violet,
		    mark=star,
		    ]
		    coordinates {
		    (10,  0.80810421349483996)(30, 0.84745259081196467)(50,0.8751719894688631)(100,0.89739411630036825)
		    };
		\legend{weather,weapons,soccer,museum,city}

		\end{axis}
	\end{tikzpicture}
\subcaption{fixing \emph{numBags}=50}\label{fig:bagsize}
\end{minipage}
\caption{Average precision and recall on museum domain.}\label{fig:bagging}
\end{figure*}

\section{Related Work \label{SEC:pw}}
\ddg{rewrite, add more}
\npr{Now the opposite: shrink please}

@@

\npr{Should I mention complex matches like 1:n and n:1 and iMap?}

@@

\bibliographystyle{aaai}
\npr{TODO: shorten citations like conference names and if there are more than 4 authors use et al}
\bibliography{main}
\end{document}
